### 2014-02-27 thesis/src/chapters/chapter-implementation.tex
Thesis: implementation summary

\newpage
\section{Summary}

>>>>

\newpage
\section{Summary}
Summing up, design of a proof-of-concept implementation of Cloud-SAP was presented. Despite the fact that it is not exhaustive, more specifically, it does not harness any prediction or advanced analysis mechanisms, it comprehensive enough to validate key points of Cloud-SAP and provide an entry point for discussions and future implementations. Although, it supports solely OpenNebula, it remains open for any cloud provider. Similarly, platform currently supports vertical scaling of CPU, horizontal scaling and scaling across multiple cloud provider, however, it is expected that next versions support wider range of actions (i.e. vertical scaling of memory, application platform tuning).
